Ethereum: A Secure Decentralised Generalised Transaction Ledger

### 2014-04-06 Paper.tex
g_0 and block chain -> blockchain

\subsection{The Block Chain Paradigm} \label{ch:overview}

@@

The world state (\textit{state}, see Appendix \ref{app:state}), is a mapping between addresses (160-bit identifiers) and account states (a data structure serialised as RLP). Though not stored on the block chain, it is assumed that the implementation will maintain this mapping in a modified Merkle Patricia tree (\textit{trie}, see Appendix \ref{app:trie}). The trie requires a simple database backend that maintains a mapping of bytearrays to bytearrays; we name this underlying database the state database. This has a number of benefits; firstly the root node of this structure is cryptographically dependent on all internal data and as such its hash can be used as a secure identity for the entire system state. Secondly, being an immutable data structure, it allows any previous state (whose root hash is known) to be recalled by simply altering the root hash accordingly. Since we store all such root hashes in the block chain, we are able to trivially revert to old states.

@@

\begin{eqnarray}
\mathbb{S}' & \equiv & \mathbb{S}_C \quad \text{except:} \\
\mathbb{S}'[s]_{balance} & \equiv & \mathbb{S}_C[s]_{balance} + r p
\end{eqnarray}

@@

$I'_D$ evaluates to the empty array. $I'_H$ and $I'_n$ have no special treatment and are determined from the block chain.

@@

The canonical block chain is a path from root to leaf through the entire block tree. In order to have consensus over which path it is, conceptually we identify the path that has had the most computation done upon it, or, the \textit{heaviest} path. Clearly one factor that helps determine the heaviest path is the block number of the leaf, equivalent to the number of blocks, not counting the unmined genesis block, in the path. The longer the path, the greater the total mining effort that must have been done in order to arrive at the leaf. This is akin to existing schemes, such as that employed in Bitcoin-derived protocols.

@@

This increases overall network security by making it much harder for an adversary to silently mine a canonical block chain (which, it is assumed, would contain different transactions to the current consensus) and dump it on the network with the effect of reversing existing blocks and the transactions within.

@@

The mining proof-of-work (PoW) exists as a cryptographically secure nonce that proves beyond reasonable doubt that a particular amount of computation has been expended in the determination of some token value $n$. It is utilised to enforce the block chain security by giving meaning and credence to the notion of difficulty (and, by extension, total difficulty). However, since mining new blocks comes with an attached reward, the proof-of-work not only functions as a method of securing confidence that the blockchain will remain canonical into the future, but also as a wealth distribution mechanism.

>>>>

\subsection{The Blockchain Paradigm} \label{ch:overview}

@@

The world state (\textit{state}, see Appendix \ref{app:state}), is a mapping between addresses (160-bit identifiers) and account states (a data structure serialised as RLP). Though not stored on the blockchain, it is assumed that the implementation will maintain this mapping in a modified Merkle Patricia tree (\textit{trie}, see Appendix \ref{app:trie}). The trie requires a simple database backend that maintains a mapping of bytearrays to bytearrays; we name this underlying database the state database. This has a number of benefits; firstly the root node of this structure is cryptographically dependent on all internal data and as such its hash can be used as a secure identity for the entire system state. Secondly, being an immutable data structure, it allows any previous state (whose root hash is known) to be recalled by simply altering the root hash accordingly. Since we store all such root hashes in the blockchain, we are able to trivially revert to old states.

@@

\begin{eqnarray}
\mathbb{S}' & \equiv & \mathbb{S}_C \quad \text{except:} \\
\mathbb{S}'[s]_{balance} & \equiv & \mathbb{S}_C[s]_{balance} + g' p
\end{eqnarray}

@@

$I'_D$ evaluates to the empty array. $I'_H$ and $I'_n$ have no special treatment and are determined from the blockchain.

@@

The canonical blockchain is a path from root to leaf through the entire block tree. In order to have consensus over which path it is, conceptually we identify the path that has had the most computation done upon it, or, the \textit{heaviest} path. Clearly one factor that helps determine the heaviest path is the block number of the leaf, equivalent to the number of blocks, not counting the unmined genesis block, in the path. The longer the path, the greater the total mining effort that must have been done in order to arrive at the leaf. This is akin to existing schemes, such as that employed in Bitcoin-derived protocols.

@@

This increases overall network security by making it much harder for an adversary to silently mine a canonical blockchain (which, it is assumed, would contain different transactions to the current consensus) and dump it on the network with the effect of reversing existing blocks and the transactions within.

@@

The mining proof-of-work (PoW) exists as a cryptographically secure nonce that proves beyond reasonable doubt that a particular amount of computation has been expended in the determination of some token value $n$. It is utilised to enforce the blockchain security by giving meaning and credence to the notion of difficulty (and, by extension, total difficulty). However, since mining new blocks comes with an attached reward, the proof-of-work not only functions as a method of securing confidence that the blockchain will remain canonical into the future, but also as a wealth distribution mechanism.
